Multi-level modelling with Openflexo/FML - A contribution to the \mpc

### 2021-05-26 5-Analysis.tex
Updates from Overleaf

@@

@@

%\emph{any disambiguations of the  case  description and assumptions made, any potentially added requirements}

\todo[inline]{quelles hypothèses supplémentaires ?}
\todo[inline]{+ architecture de la modélisation (ce qui se trouve dans le ppt), le détail se retrouvera dans la section suivante}

%Joel commence

% Sylvain
% Joel, je te propose les deux figures suivantes:

>>>>

%\emph{Analysis: any disambiguations of the  case  description and assumptions made, any potentially added requirements}

@@

Based on this approach, we organize our set of models as presented by the figure \ref{fig:MultilevelArchitecture}. The resulted multi-level architecture is organized as a set of VirtualModels. The first one is the core concepts model including the definition of Processes and Tasks. The second one, Acme VirtualModel, is extended from the previous model to integrate the Acme definitions. Our FML language defines the multiple inheritance concept between VirtualModels as illustrated in the section \ref{sec:AcmeSoftwareDevelopmentProcess}.

Finally as explained previously, the defined level for the Acme model and the XSure is the result of the instantiation of VirtualModels of different levels. In our approach this level can't be specialized or extended but all the other VirtualModels could be extended  by any concepts, as a new federated model.

@@

\todo[inline]{quelles hypothèses supplémentaires ?}
%\todo[inline]{+ architecture de la modélisation (ce qui se trouve dans le ppt), le détail se retrouvera dans la section suivante}
